## circplot

[![R-CMD-check](https://github.com/kbroman/circplot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kbroman/circplot/actions/workflows/R-CMD-check.yaml)
[![r-universe badge](https://kbroman.r-universe.dev/circplot/badges/version)](https://kbroman.r-universe.dev/circplot)
[![zenodo DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.20097110.svg)](https://doi.org/10.5281/zenodo.20097110)

R package to facilitate making plots as circles.

Created this for the function `plot_scan1_circ()`, for plotting a genome scan
as a circle, and for making fun of circle plots.

---

### Installation

Install circplot from
[R-universe](https://kbroman.r-universe.dev/circplot):

```{r install_runiverse, eval=FALSE}
install.packages("circplot", repos="https://kbroman.r-universe.dev")
```

Install from github using the [remotes](https://remotes.r-lib.org)
package:

```{r install_github, eval=FALSE}
install.packages("remotes")
remotes::install_github("kbroman/circplot")
```

---

### Usage

The function `xy2circ()` converts (x,y) coordiates to circular
coordinates. It is used internally in the function
`plot_scan1_circ()`.

```{r plot_scan1_circ}
library(circplot)
library(qtl)
suppressMessages(library(qtl2))
data(hyper)
hyper <- convert2cross2(hyper)

map <- insert_pseudomarkers(hyper$gmap, step=0.2)
pr <- calc_genoprob(hyper, map, err=0.01)
out <- scan1(pr, hyper$pheno)

par(mar=rep(0,4))
plot_scan1_circ(out, map, lwd=3, rlim=c(5,7))
```

---

### License

Licensed under [GPL-3](https://www.r-project.org/Licenses/GPL-3).
